
Models used for time series prediction comprise one of the most important methods in economic forecasting. In particular, time series forecasting is important in the study of financial markets. Yet these models are frequently poorly performing, and accurate time-series forecasting is considered a `'top 10 problem" in data mining. \cite{YW} Moreover, markets tend to price in known information, and as a result it is difficult to discern any pattern in a market's movements without material nonpublic information. \cite{r} This is known as the "no arbitrage principle," and makes financial time series particularly vexing to predict.

While neural networks have been studied for applicability to time series data since at least the early 1990s, \cite{Azoff} many of these applications deal with contexts which are not subject to the no arbitrage principle (for example, forecasting crop yields or water levels) and do not experience the concomitant reduction of predictability in the data. A recent review of the literature is provided by Längkvist et al., who note applicability of techniques such as recurrent neural networks with LSTM. \cite{Lankvist} Logically, the long-term dependency recognition capacities that enable LSTM models to predict NLP outcomes with high success may translate to pattern recognition in the financial markets. It is well known, for instance, that cycles in the overall market are characterized by a particular geometry, with downturns exhibiting greater volatility in returns.

Previous research has noted the particular difficulty of forecasting cryptocurrency markets given their unusual volatility, and we look forward to accommodating this challenge. \cite{ian} To this end, we plan to implement RNN techniques, including RNN/LSTM learning on the residuals of vector autoregressive models, a hybrid method that has been successful in the literature. \cite{r2n2} We use Statsmodels and PyTorch for this purpose. 

We also hope to gain intuitive insight into the macrostructure of the cryptocurrency trading markets, enabling us to answer questions about capital flow into, out of, and within the cryptocurrency space. This exploration could add a quantitative voice to a conversation about the market which has been investigated from ecological \cite{ecology} and structural \cite{structure} perspectives. 